### 2004-07-06 Documentation/part1.tex
*** empty log message ***

\begin{table}[tp]
\begin{tabular}{p{4.2cm}p{5.5cm}p{5.1cm}}
\hline
Function & Purpose & Parameters $\rightarrow$ Result\\
\hline
\GLB{glbAllocProjection} & Create projection vector & {\tt ()} \\
\GLB{glbFreeProjection} & Destroy projection vector {\tt stale} & {\tt (glb\_projection stale)} \\
\GLB{glbDefineProjection} & Assign projection vector {\tt in} & {\tt (glb\_projection in, int theta12, int theta13, int theta23, int delta, int dms, int dma)} \\ 
\GLB{glbCopyProjection} & Copy vector {\tt source} to {\tt dest} & {\tt (const glb\_projection source, glb\_projection dest)} \\
\GLB{glbPrintProjection} & Print vector {\tt in} to file {\tt stream} & {\tt (FILE* stream, const glb\_projection in)} \\
\GLB{glbSetProjectionFlag} & Set flag for oscillation parameter {\tt which} in vector {\tt in} to value {\tt flag}. & {\tt (glb\_projection in, int flag, int which)} \\
\GLB{glbGetProjectionFlag} & Return flag for oscillation parameter {\tt which} in vector {\tt in}. & {\tt (const glb\_projection in, int which)} $\rightarrow$ {\tt int} flag \\
\GLBNS{glbSetDensityProjectionFlag} {\tt glbSetDensity-} \newline {\tt ProjectionFlag}  & Set flag for density parameter {\tt which} in vector {\tt in} to value {\tt flag}. & {\tt (glb\_projection in, int flag, int which)} \\
\GLBNS{glbGetDensityProjectionFlag} {\tt glbGetDensity-} \newline {\tt ProjectionFlag} & Return flag for density parameter {\tt which} in vector {\tt in}.  & {\tt (const glb\_projection in, int which)} $\rightarrow$ {\tt int} flag \\
\hline
\end{tabular}
\caption{\label{tab:defprojection} Different functions handling the
\GLB{glb\_projection} type. Flags are either \GLB{GLB\_FIXED} or \GLB{GLB\_FREE}.}
\end{table}

In principle, one can also use three- or more-dimensional projections. In addition, one may want to use any other set of parameters for single- or two-parameter projections. The function \GLB{glbChiNP} is designed for this purpose.

WW: CONTINUE HERE

glb\_projection type: exactly similar to glb\_params (return values)

Functions in table: komische Aufteilung

Hint on example.

>>>>

\begin{table}[t!]
\begin{tabular}{p{4.2cm}p{5.5cm}p{5.1cm}}
\hline
Function & Purpose & Parameters $\rightarrow$ Result\\
\hline
\GLB{glbAllocProjection} & Create projection vector & {\tt ()} \\
\GLB{glbFreeProjection} & Destroy projection vector {\tt stale} & {\tt (glb\_projection stale)} \\
\GLB{glbDefineProjection} & Assign projection vector {\tt in} & {\tt (glb\_projection in, int theta12, int theta13, int theta23, int delta, int dms, int dma)} \\ 
\GLB{glbCopyProjection} & Copy vector {\tt source} to {\tt dest} & {\tt (const glb\_projection source, glb\_projection dest)} \\
\GLB{glbPrintProjection} & Print vector {\tt in} to file {\tt stream} & {\tt (FILE* stream, const glb\_projection in)} \\
\GLB{glbSetProjectionFlag} & Set flag for oscillation parameter {\tt which} in vector {\tt in} to value {\tt flag}. & {\tt (glb\_projection in, int flag, int which)} \\
\GLB{glbGetProjectionFlag} & Return flag for oscillation parameter {\tt which} in vector {\tt in}. & {\tt (const glb\_projection in, int which)} $\rightarrow$ {\tt int} flag \\
 {\tt glbSetDensity\-ProjectionFlag} \GLBNS{glbSetDensityProjectionFlag} & Set flag for density parameter {\tt which} in vector {\tt in} to value {\tt flag}. & {\tt (glb\_projection in, int flag, int which)} \\
{\tt glbGetDensity\-ProjectionFlag} \GLBNS{glbGetDensityProjectionFlag} & Return flag for density parameter {\tt which} in vector {\tt in}.  & {\tt (const glb\_projection in, int which)} $\rightarrow$ {\tt int} flag \\
\hline
\end{tabular}
\caption{\label{tab:defprojection} Different functions handling the
\GLB{glb\_projection} type. Flags are either \GLB{GLB\_FIXED} or \GLB{GLB\_FREE}. The (unshown) return values of the {\tt Set-} and {\tt Define-} functions point either to the assigned vector if successful, or they are {\tt NULL} if unsuccessful.}
\end{table}

In principle, one can also use three- or more-dimensional projections. In addition, one may want to use a different set of parameters for single- or two-parameter projections. The very flexible function \GLB{glbChiNP} is
designed for this purpose. However, because of its flexibility, it 
involves more sophistication.

In order to define arbitrary projections, we introduce the vector
\GLB{glb\_projection}, which is very similar to the
oscillation parameter vector {\tt glb\_params}.
Normally, the user does not need to access this type directly:
A set of function similar to the ones for {\tt glb\_params} is
provided. The purpose of {\tt glb\_projection} is to tell \GLOBES\ 
what parameters are fixed, and what are minimized over. Thus, in
comparison to {\tt glb\_params}, it does not take values for the
parameters, but flags \GLB{GLB\_FIXED} or \GLB{GLB\_FREE}.
For example, the projection onto the $\theta_{13}$-axis {\tt glbChiTheta}
is nothing else than a special case of {\tt glbChiNP} with $\theta_{13}$
fixed and all the other parameters free. Similar to {\tt glb\_params},
the type {\tt glb\_projection} has to be created first, and destroyed
later. The access functions for {\tt glb\_projection} are summarized in \Tab~\ref{tab:defprojection}. Since the complete set is very similar to
the one for {\tt glb\_params}, we do not go into greater details here.

As soon as we have defined a projection, we can assign it:
\begin{function}
\GLBNS{glbSetProjection}
{\tt int glbSetProjection(const glb\_projection in)} sets the projection
to {\tt in}. The return value is $0$ if successful, and $-1$ if
unsuccessful.
\end{function}
Similarly, the currenty assigned projection can be returned with:
\begin{function}
\GLBNS{glbGetProjection}
{\tt int glbGetProjection(glb\_projection out)} writes the currently
set projection to {\tt out}. The return value is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
After setting the starting values, input errors, and the projection, 
we can run the minimizer:
\begin{function}
\GLBNS{glbChiNP}
{\tt double glbChiNP(const glb\_params in, glb\_params out, int exp)} 
returns the projected $\chi^2$ onto the hyperplane specified by 
{\tt glbSetProjection} for the  experiment {\tt exp}. 
For the simulation of all initialized experiments,
use {\tt GLB\_ALL} for {\tt exp}. The values in {\tt in} are the guessed fit values for the minimizer (all free parameters) and the fit values
on the hyperplane (all fixed parameters). The actually determined parameters at the minimum are returned in {\tt out}, where the fixed parameters are still at their input values. If {\tt out} is set to {\tt NULL}, this information will not be returned.
\end{function}
As an example, the projection sequence for a minimization over
$\deltacp$ only looks like this:
\begin{quote}
{\tt
  glb\_projection th13\_projection = glbAllocProjection(); \\
  glbDefineProjection(th13\_projection,GLB\_FIXED,GLB\_FIXED,GLB\_FIXED,\\
  \hspace*{2cm} GLB\_FREE,GLB\_FIXED,GLB\_FIXED); \\
  glbSetProjection(th13\_projection); \\ 
  res1=glbChiNP(test\_values,NULL,GLB\_ALL); \\
  glbFreeProjection(th13\_projection);
}
\end{quote}
In this case, only the correlation with $\deltacp$ is taken into account.
Note that in the  example on page~\pageref{ex:corrproj} this projection
is compared with the result including the full multi-parameter correlation.
